Deckard: A Declarative Tool for Machine Learning Robustness Evaluations

### 2025-05-06 paper.tex
bibliography tweaks in .tex file

\title{Deckard: A Declarative Tool for Machine Learning Robustness
Evaluations}
\author{}
\date{\vspace{-2.5em}15 October 2024}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-tensorflow}{}}%
Abadi, Martín, Ashish Agarwal, Paul Barham, Eugene Brevdo, Zhifeng Chen,
Craig Citro, Greg S. Corrado, et al. 2015. {``{TensorFlow}: Large-Scale
Machine Learning on Heterogeneous Systems.''}
\url{https://www.tensorflow.org/}.

\leavevmode\vadjust pre{\hypertarget{ref-optuna}{}}%
Akiba, Takuya, Shotaro Sano, Toshihiko Yanase, Takeru Ohta, and Masanori
Koyama. 2019. {``Optuna: A Next-Generation Hyperparameter Optimization
Framework.''} In \emph{Proceedings of the 25th ACM SIGKDD International
Conference on Knowledge Discovery \& Data Mining}, 2623--31.

@@

\leavevmode\vadjust pre{\hypertarget{ref-extraction_attack}{}}%
Jagielski, Matthew, Nicholas Carlini, David Berthelot, Alex Kurakin, and
Nicolas Papernot. 2020. {``High Accuracy and High Fidelity Extraction of
Neural Networks.''} In \emph{29th USENIX Security Symposium (USENIX
Security 20)}, 1345--62.

@@

\leavevmode\vadjust pre{\hypertarget{ref-meyers2024massively}{}}%
Meye. 2024. {``Massively Parallel Evasion Attacks and the Pitfalls
of Adversarial Retraining.''} \emph{EAI Endorsed Transactions on
Internet of Things} 10.

>>>>

\title{Deckard: A Declarative Tool for Machine Learning Robustness
Evaluations}
\author{}
\date{\vspace{-2.5em}15 April 2025}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-tensorflow}{}}%
Abadi, Martín, Ashish Agarwal, Paul Barham, Eugene Brevdo, Zhifeng Chen,
Craig Citro, Greg S. Corrado, et al. 2015. {``{TensorFlow}: Large-Scale
Machine Learning on Heterogeneous Systems.''}

\leavevmode\vadjust pre{\hypertarget{ref-optuna}{}}%
Akiba, Takuya, Shotaro Sano, Toshihiko Yanase, Takeru Ohta, and Masanori
Koyama. 2019. {``Optuna: A Next-Generation Hyperparameter Optimization
Framework.''} In \emph{Proceedings of the 25th ACM SIGKDD}, 2623--31.

@@

\leavevmode\vadjust pre{\hypertarget{ref-extraction_attack}{}}%
Jagielski, Matthew, Nicholas Carlini, David Berthelot, Alex Kurakin, and
Nicolas Papernot. 2020. {``High Accuracy and High Fidelity Extraction of
Neural Networks.''} In \emph{29th USENIX Security Symposium}, 1345--62.

@@

\leavevmode\vadjust pre{\hypertarget{ref-meyers2024massively}{}}%
Meyers, C et al. 2024. {``Massively Parallel Evasion Attacks and the Pitfalls
of Adversarial Retraining.''} \emph{EAI Endorsed Transactions on
Internet of Things} 10.
